Competition

### 2020-09-23 R/competition wrangling.Rmd
filtered out plants near edges

```{r}
add_density_cols <- function(df, L, U, by, verbose = FALSE) {

@@

  df_out <- 
    future_map_dfr(1:nrow(df), function(r) { #loop through rows/plants
      #get coordinates for that plant
      focal_plant <- t(df[r, c("x", "y")])

      #calculate distance to every other plant
      focal_df <-
        df %>%
        rowwise() %>%
        mutate(dist = eu_dist(focal_plant, c(x, y)))

      #get total number of shoots at every ring
      future_map2_dfc(lag(d)[-1], d[-1],
               ~ transmute(focal_df,
                           !!glue("shts_{.x}_{.y}") := shts * (dist > .x & dist <= .y))) %>%
        ungroup() %>% 
        summarize(across(everything(), ~sum(., na.rm = TRUE)))
    })

@@

```{r}
ha_xy2 <-
  ha_xy %>% 
  group_by(plot, year) %>% 
  group_split() %>% 
  # head() %>% #test with 6 df to see how long it will take.
  future_map(~{
      add_density_cols(.x, L = 0, U = 10, by = 5) 
    }) %>% 
  bind_rows()
beepr::beep(4)
```
```{r}
ha_xy2
```

@@

## Remove plants on edge

I should remove plants on the edge because the entire "donut" isn't included for them.  I can do this by finding the distance to the nearest edge, then checking if that distance is greater than the outer radius for the donuts, and if so, setting that density value to NA.

To do this, I think I need to know how big the plots are.  Should have kept the plot_x and plot_y variables, maybe.

```{r}

>>>>

```{r}
# df <- y1p1
# L = 0
# U = 10
# by = 0.5
add_density_cols <- function(df, L, U, by, na_edges = TRUE) {

@@

  df_out <- 
    future_map_dfr(1:nrow(df), function(r) { #loop through rows/plants
      #get coordinates for that plant
      focal_plant <- t(df[r, c("x", "y")])
      # focal_plant <- c(0,0)

      if (na_edges) {
        #don't do calculations for rings that go outside the plot
        edge_dist <- min(c(focal_plant, c(100, 50) - focal_plant))
        d2 <- d[which(d < edge_dist)]
      } else {
        d2 <- d
      }

      #calculate distance to every other plant
      focal_df <-
        df %>%
        rowwise() %>%
        mutate(dist = eu_dist(focal_plant, c(x, y))) %>% 
        ungroup()

      # If plant is near edge, return NAs

      #get total number of shoots at every ring
      if (length(d2) > 1) {
        future_map2_dfc(lag(d2)[-1], d2[-1],
                        ~ transmute(
                          focal_df,
                          !!glue("shts_{.x}_{.y}") :=
                            shts * (dist > .x & dist <= .y)
                        )
        ) %>% 
          #excludes focal plant with dist == 0
          summarize(across(everything(), ~sum(., na.rm = TRUE)), .groups = "drop")
      } else {
        # if all the rings go outside the plot, then return an empty row
        tibble_row()
      }
    })

@@

```{r}
ha_xy2 <-
  ha_xy %>% 
  group_by(plot, year) %>% 
  group_split() %>% 
  # head() %>% #test with 6 df to see how long it will take.
  future_map(~{
      add_density_cols(.x, L = 0, U = 10, by = 0.5) 
    }) %>% 
  bind_rows()
beepr::beep(4)
```

Aggregate some of the distances for simpler modeling.

```{r}
ha_xy3 <-
  ha_xy2 %>% 
  rowwise() %>%
  mutate(shts_0_5 = sum(c_across(shts_0_0.5:shts_4.5_5)),
         shts_5_10 = sum(c_across(shts_5_5.5:shts_9.5_10)))

ha_density <- ha_xy3
```

@@

# Write to file

```{r}
write_rds(ha_density, here("analysis", "data", "derived_data", "ha_density.rds"))
```
